Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2023-06-13 Writing/manuscript_gwr.rmd
supplementary appendix modified

---
title: "Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
---

@@

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low"] %>%
  .[pRatio == 6.56, pLabel := "Middle"] %>%
  .[pRatio == 7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]

>>>>

---
title: "Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    base_format: "bookdown::word_document2"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
---

@@

#* read the results rds file
results <-
  here("Shared/Results/gaussian/pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low"] %>%
  .[pRatio == 6.56, pLabel := "Middle"] %>%
  .[pRatio == 7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
